Sequential Monte Carlo methods (also called particle filters) provide a
natural computational approach for state and parameter estimation
problems in the context of nonlinear evolution equations. Yet the
curse of dimensionality prevents particle filters to be employed for
systems with a high-dimensional state space [2]. One option to
overcome this limitation is to use localization techniques. However,
due to the random resampling steps of standard particle filters,
localization cannot be applied in a straightforward manner. The
recently proposed ensemble transform particle filter (ETPF) [4]
provides a solution to this problem and replaces the resampling step
of a standard particle filter by a linear transformation. Further, this
linear transformation of the particles allows to design a hybrid
approach that couples particle filters with ensemble Kalman filters
[3]. However, the transformation step is computationally expensive
and leads to an underestimation of the ensemble spread for small
and moderate ensemble sizes.
These shortcomings have recently been addressed in [1] by
developing second-order accurate extensions of the ETPF. These
improvements allow one in particular to replace the exact solution of
a linear transport problem by its Sinkhorn approximation. It is also
demonstrated that the nonlinear ensemble transform filter (NETF) [6,
5] arises as a special case of our general framework. Numerical
results for the Lorenz-63 and Lorenz-96 models demonstrate the
effectiveness of the proposed modified particle filters.

Joint work with Sebastian Reich and Walter Acevedo.
\\
\\
\noindent References
\\
\\
\noindent [1] W. Acevedo, J. de Wiljes, and S. Reich, A second-order accurate
ensemble transform particle filter, accepted at SIAM J. Sci Comp,
https://arxiv.org/abs/1608.08179 (2017).

\noindent [2] T. Bengtsson, P. Bickel, and B. Li, Curse of dimensionality
revisited: Collapse of the particle filter in very large scale systems, in
IMS Lecture Notes - Monograph Series in Probability and Statistics:
Essays in Honor of David F. Freedman, vol. 2, Institute of
Mathematical Sciences, 2008, pp. 316–334.

\noindent [3] N. Chustagulprom, S. Reich, and M. Reinhardt, A hybrid ensemble
transform filter for nonlinear and spatially extended dynamical
systems, SIAM/ASA J. Uncertainty Quantification, 4 (2016), pp. 592–608.

\noindent [4] S. Reich, A nonparametric ensemble transform method for
Bayesian inference, SIAM J. Sci. Comput., 35 (2013), pp. A2013–
A2024.

\noindent [5] J. Tödter and B. Ahrens, A second-order exact ensemble square
root filter for nonlinear data assimilation, Mon. Wea. Rev., 143
(2015), pp. 1347–1367.

\noindent [6] X. Xiong, I. Navon, and B. Uzungoglu, A note on the particle filter
with posterior Gaussian resampling, Tellus, 85A (2006), pp. 456–460.
