\documentclass[12pt]{article}

\usepackage{amsmath}
\usepackage{url}
\newcommand{\postertitle}[1]{{\Large\bf #1}\\[12pt]}
\newcommand{\authors}[1]{\emph{#1}\\}
\newcommand{\affiliations}[1]{{#1}\\}
\newcommand{\contacts}[1]{{#1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\begin{center}
\vspace*{0.5cm}
%
\postertitle{Accelerating MCMC with an approximation - Importance sampling versus delayed acceptance}
%
\authors{Jouni Helske$^\star$, Matti Vihola and Jordan Franks} % please mark the name of the person(s) presenting the poster with a star
% 
\affiliations{Department of Mathematics and Statistics, University of Jyv{\"a}skyl{\"a}}
%
\contacts{jouni.helske@iki.fi} % URL or email address of contact person
%
\vspace*{0.3cm}
\end{center}

%%%%%%%%%%   Type your abstract below
We consider importance sampling (IS) type weighted estimators, based 
on Markov chain Monte Carlo (MCMC) which targets an approximate
marginal of the target distribution \cite{vihola-helske-franks}. The IS approach, based on
unbiased estimators, is consistent, and provides a natural alternative
to delayed acceptance (DA) pseudo-marginal/particle MCMC  \cite{christen-fox}. The IS approach
enjoys many benefits against DA, including a straightforward
parallelisation and additional flexibility in MCMC implementation. We compare the computational efficiency of IS and DA approaches in a geometric Brownian motion setting where the IS approach provides substantial efficiency improvements over DA.

%%%%%%%%%%%   References
%If you have references, you can produce a .bbl file using bibtex
%and copy/paste thebibliography here
\begin{thebibliography}{1}	
	
	\bibitem{christen-fox}
    J.~Andr{\'e}s Christen and Colin Fox.
	\newblock Markov chain {M}onte {C}arlo using an approximation.
	\newblock {\em Journal of Computational and Graphical Statistics.}, 14(4), 2005.
	
	\bibitem{vihola-helske-franks}
	Matti Vihola, Jouni Helske, and Jordan Franks.
	\newblock Importance sampling type correction of {M}arkov chain {M}onte {C}arlo
	and exact approximations.
	\newblock Preprint arXiv:1609.02541, 2016.
\end{thebibliography}


\end{document}
