\documentclass[12pt]{article}

\usepackage{amsmath}
\usepackage{url}
\newcommand{\postertitle}[1]{{\Large\bf #1}\\[12pt]}
\newcommand{\authors}[1]{\emph{#1}\\}
\newcommand{\affiliations}[1]{{#1}\\}
\newcommand{\contacts}[1]{{#1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\begin{center}
\vspace*{0.5cm}
%
\postertitle{Terrain Navigation using the Ambient Magnetic Field as a Map}
%
\authors{Arno Solin$^\star$} % please mark the name of the person(s) presenting the poster with a star
% 
\affiliations{Department of Computer Science, Aalto University}
%
\contacts{\url{http://arno.solin.fi}} % URL or email address of contact person
%
\vspace*{0.3cm}
\end{center}

%%%%%%%%%%   Type your abstract below
%The abstract goes here. Maybe with a reference \cite{label} and some math:
%\begin{align*}
%	\exp(i\pi) = -1
%\end{align*}

Variations in the ambient magnetic field can be used as features in indoor positioning and navigation. Here a probabilistic Gaussian process regression based framework \cite{Solin+Kok+Wahlstrom+Schon+Sarkka:accepted} is used for composing the vector field magnetic map. The map matching (positioning) is based on a particle filter \cite{Solin+etal:2016}, and follows the classical terrain matching framework used in aircraft positioning and navigation. The feasibility of this terrain matching approach is demonstrated in real-life indoor positioning examples, where both the mapping and positioning are done using a smartphone.


%%%%%%%%%%%   References
%If you have references, you can produce a .bbl file using bibtex
%and copy/paste thebibliography here
\begin{thebibliography}{1}
\bibitem[1]{Solin+Kok+Wahlstrom+Schon+Sarkka:accepted}
  A.~Solin, M.~Kok, N.~Wahlstr{\"o}m, T.~B.~Sch{\"o}n,
  and S.~S{\"a}rkk{\"a}.
\newblock Modeling and interpolation of the ambient magnetic field by
  {G}aussian processes.
\newblock {Accepted for publication in IEEE Transactions on Robotics}.

\bibitem[2]{Solin+etal:2016}
  A.~Solin, J.~Kannala, S.~S\"arkk\"a, and E.~Rahtu.
\newblock Terrain navigation in the magnetic landscape: {P}article filtering
  for indoor positioning.
\newblock In \emph{European Navigation Conference (ENC)}, pages 1--9. IEEE,
  2016.

\end{thebibliography}


\end{document}
