\documentclass[12pt]{article}

\usepackage{amsmath}
\usepackage{url}
\newcommand{\postertitle}[1]{{\Large\bf #1}\\[12pt]}
\newcommand{\authors}[1]{\emph{#1}\\}
\newcommand{\affiliations}[1]{{#1}\\}
\newcommand{\contacts}[1]{{#1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\begin{center}
\vspace*{0.5cm}
%
\postertitle{A probabilistic scheme for joint parameter estimation and state 
prediction in complex dynamical systems}
%
\authors{Sara Vieites} % please mark the name of the person(s) presenting the poster with a star
% 
\vspace*{0.3cm}
\end{center}

Many problems in the geophysical sciences demand the ability 
to calibrate the parameters and predict the time evolution of complex 
dynamical models using sequentially-collected data. Here we introduce a 
general methodology for the joint estimation of the static parameters 
and the forecasting of the state variables of nonlinear, and possibly 
chaotic, dynamical models. The proposed scheme is essentially 
probabilistic. It aims at recursively computing the sequence of joint 
posterior probability distributions of the unknown model parameters and 
its (time varying) state variables conditional on the available 
observations. The latter are possibly partial and contaminated by noise. 
The new framework combines a Monte Carlo scheme to approximate the 
posterior distribution of the  fixed parameters with fi ltering (or data 
assimilation) techniques to track and predict the distribution of the 
state variables. For this reason, we refer to the proposed methodology 
as nested  filtering. In this paper we speci cally explore the use of 
Gaussian  filtering methods, but other approaches fi t naturally within 
the new framework. As an illustrative example, we apply three different 
implementations of the methodology to the tracking of the state, and the 
estimation of the fi xed parameters, of a stochastic two-scale Lorenz 96 
system. This model is commonly used to assess data assimilation 
procedures in meteorology. For this example, we compare different nested 
fi lters and show estimation and forecasting results for a 
4,000-dimensional system.



\end{document}
